The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-17 analysis/paper/paper.qmd
Make small style corrections
Accept md changes made by the RStudio visual editor
Correct cache code chunk label

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache:true

@@

emu_theses$text_clean <- emu_theses$text %>%
  clean_basic() %>%
  str_remove_all(find_meta_stopwords(emu_theses) )  
```

>>>>

```{r}
#| label: extract-pdf-text
#| echo: false
#| cache: true

@@

emu_theses$text_clean <- emu_theses$text |> 
  clean_basic() |> 
  str_remove_all(find_meta_stopwords(emu_theses) )  
```
